---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/ropenscilabs/available.svg?branch=master)](https://travis-ci.org/ropenscilabs/available)

# available

The goal of available is to help you choose a good name for your R package. It helps you determine if the package name you are considering is available to use (on GitHub, CRAN and Bioconductor), checks Urban Dictionary to make sure you haven't unintentionally chosen a bad word, searches for the name on Wikipedia, checks the sentiment of your chosen name and lets you know about packages with similar names. It can also suggest a possible names for your package based on its title or a short description of what it does.

## Installation

You can install available from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropenscilabs/available")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
available::available("available")
```

### Rstudio Support
In order to have color in the RStudio terminal you need a [daily build of
RStudio](https://dailies.rstudio.com/) and development versions of the
**rstudioapi** and **crayon** packages.

```r
devtools::install_github("rstudio/rstudioapi")
devtoosl::install_github("gaborcsardi/crayon")
```
